Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-14 paper.tex
Clean up introduction some more

If numerical models are validated with physical model data that was obtained at
insufficiently high Reynolds numbers, it cannot be determined whether problems
with model predictions are caused by Reynolds number effects, other turbine
parameters or issues with the numerical model itself. One might also obtain
different predictions of scaled systems due to modified physics at lower
Reynolds numbers, e.g., laminar boundary layers and transitional flow regimes.
If the numerical model is then considered ``validated,'' there is a risk that
its application at full-scale may produce incorrect predictions. As such, it is
questionable whether numerical models validated with physical model data
obtained at Reynolds numbers orders of magnitude away from prototype scale
should be considered validated at all.

Uncertainty from scale effects can potentially be overcome by showing that a
scaled physical model test has become Reynolds number independent, and therefore
validation efforts should be relevant at full scale. It is therefore of interest
how small---since size, or scale generally correlates inversely with cost---the
model can be while remaining a reliable predictor of full-scale behavior. At the
very least, it is necessary to test at a scale where results can be
extrapolated, i.e., changes are occurring quasi-linearly without dramatic
changes in the underlying physical principles governing the behavior of
interest, e.g., power production in the case of a wind or MHK turbine.

>>>>

If numerical models are validated with physical model data that was obtained at
insufficiently high Reynolds numbers, it cannot be determined whether problems
with model predictions are caused by Reynolds number effects, other turbine
geometrical or operating parameters, or issues with the numerical model itself.
One might also obtain different predictions for scaled systems due to modified
physics at lower Reynolds numbers, e.g., laminar boundary layers and
transitional flow regimes. If the numerical model is then considered
``validated,'' there is a risk that its application at full-scale may produce
incorrect predictions. As such, it is questionable whether numerical models
validated with physical model data obtained at Reynolds numbers orders of
magnitude away from prototype scale should be considered validated at all.

Uncertainty from scale effects can potentially be overcome by showing that a
scaled physical model test has become Reynolds number independent, and therefore
validation efforts should be relevant at full scale. It is therefore of interest
how small---since physical model size or facility flow speed generally correlate
with cost---the model can be while remaining a reliable predictor of full-scale
behavior. At the very least, it is necessary to test at a scale where results
can be extrapolated, i.e., changes are occurring quasi-linearly without dramatic
changes in the underlying physical principles governing the behavior of
interest, e.g., power production in the case of a wind or MHK turbine.
